### 2025-03-11 ms.qmd
updates

```{r, model_sem}
#| label: model_sem
# Making the SEM model by using a multivariate brms. The aim is to test the relationships between mitochondrial physiology and detection latency.
# Learning here was evaluated obtaining the learning slopes for each individual (see data_process.R).
# All continue variables were standardized (var/2SD) before running the models (see data_process.R). 
#
source(here("R", "func.R"))
#
refit <- FALSE
#
if(refit){
  m_SEM <- brm(
    bf(slope_mean + slope_sd ~ mit_density + mit_potential + DNAdamage + peroxidation + (1|clutch)) +
    bf(mean_dnadamage ~ ROS + (1|clutch)) +
    bf(peroxidation ~ ROS + (1|clutch)) +
    bf(mean_ros ~ mit_density + mit_potential + (1|clutch)) +
  set_rescor(TRUE),
  family = gaussian(),
  data = clean_df, 
  chains = 4, cores = 4, iter = 8000, warmup = 2000,
  control = list(adapt_delta = 0.99, max_treedepth = 11))
  # Save the model
  saveRDS(m_SEM, file = here("output/models/m_SEM.rds"))
} else {
  m_SEM <- readRDS(here("output/models/m_SEM.rds"))
}
```

>>>>

```{r, model_sem}
#| label: model_sem
# Making the SEM model by using a multivariate brms. The aim is to test the relationships between mitochondrial physiology and detection latency.
# Learning here was evaluated obtaining the learning slopes for each individual (see data_process.R).
# All continue variables were standardized (var/2SD) before running the models (see data_process.R). 
#
source(here("R", "func.R"))
#
refit <- FALSE
#
data_SEM <- clean_df %>%
  mutate(obs = 1:nrow(.),
        vec = rep(1, length(obs)))
if(refit){
  m_SEM <- brm(
    bf(slope_mean | se(slope_sd, sigma = FALSE) ~ mit_density + mit_potential + DNAdamage + peroxidation + (1|clutch) + (1|q|obs)) +
    bf(DNAdamage | se(vec, sigma = FALSE) ~ ROS + (1|clutch)+ (1|p|obs)) +
    bf(peroxidation | se(vec, sigma = FALSE) ~ ROS + (1|clutch) + (1|p|obs)) +
    bf(ROS | se(vec, sigma = FALSE) ~ mit_density + mit_potential + (1|clutch) + (1|t|obs)) +
  set_rescor(FALSE),
  family = gaussian(),
  data = data_SEM, 
  chains = 4, cores = 4, iter = 8000, warmup = 2000,
  control = list(adapt_delta = 0.99, max_treedepth = 11))
  # Save the model
  saveRDS(m_SEM, file = here("output/models/m_SEM.rds"))
} else {
  m_SEM <- readRDS(here("output/models/m_SEM.rds"))
}
```
